---
title: "An Exploration of Medical Data"
---

## Motivation and Context

My original motivation for choosing this dataset was a personal interest in medicine. Additionally, I am likely to be working with health data in the future, as I have the goal of working in the insurance industry. This dataset contains information on patients with a

```{r}
#| label: do this first
#| echo: false
#| message: false

here::i_am("math-437-project-template.qmd")
```

## Main Objective

The main objective of this analysis is to predict the likelihood of recovery for a patient suffering from one of the listed lung conditions, given known factors such as age, smoking status, and lung capacity.

## Packages Used In This Analysis

```{r}
#| label: load packages
#| message: false
#| warning: false

library(here)
library(readr)
library(dplyr)
library(ggplot2)
library(rsample)
library(naniar)
library(mice)
library(parsnip)
library(yardstick)
```

| Package | Use |
|--------------------------------|----------------------------------------|
| [here](https://github.com/jennybc/here_here) | to easily load and save data |
| [readr](https://readr.tidyverse.org/) | to import the CSV file data |
| [dplyr](https://dplyr.tidyverse.org/) | to massage and summarize data |
| [rsample](https://rsample.tidymodels.org/) | to split data into training and test sets |
| [ggplot2](https://ggplot2.tidyverse.org/) | to create nice-looking and informative graphs |
| [naniar](https://naniar.njtierney.com/) | to summarize and visualize missing data |
| [mice](https://github.com/amices/mice) | to impute missing values |
| [parsnip](https://parsnip.tidymodels.org/) | to create the model with the data |
| [yardstick](https://yardstick.tidymodels.org/) | to measure the model's performance |

## Data Description

This data was found on [Kaggle](https://www.kaggle.com/datasets/samikshadalvi/lungs-diseases-dataset/data), and was reportedly obtained via web scraping off of the websites of three lung clinics in the Indiana area.

```{r}
#| label: import data
#| warning: false

lung_disease <- readr::read_csv(here::here("lung_disease_data.csv"))
```

### Data Limitations

There are many limitations as to the effectiveness of this data in modeling a general population. The data itself was collected through questionable methods with little documentation, and was possibly even synthesized. Other factors, such as the unusual distribution of patient ages and the uniformity of the recovery rates across different diseases, which will be explored shortly, provide further support for the possibility.

###  **Data Wrangling (Optional Section)**

The only data wrangling that this dataset requires is separation of the training and test sets, and accounting the missing values. The latter will be done after the EDA, to determine whether they should be imputed or omitted, and how, while the former must be done after the missing values are accounted for.

## Exploratory Data Analysis

We will first look at the missing parts of the data, to determine if there are any visible patterns or correlations in the missing data points that will be informative. A simple plot shows that the data seems to be missing at random, with little correlation between variables. Such a uniform distribution of missing values is not consistent with real-life data collection.

```{r}
vis_miss(lung_disease)
```

There are a few other inconsistencies in this dataset, which can be seen when examining the data more closely. A look at the recovery rates for each disease shows the following:

```{r}
lung_disease %>%
  select(Recovered,`Disease Type`) %>% 
    na.omit() %>% 
    count(Recovered, `Disease Type`) %>%   
    group_by(`Disease Type`) %>%
    mutate(percent_recovered = prop.table(n) * 100) %>%
  filter(Recovered == "Yes")
```

We can see that the proportion of patients who successfully recovered is approximately 50% for each disease. This is, of course, inconsistent with the real-life rates of recovery for these diseases.

## Modeling

## Insights

### Limitations and Future Work

### Reflection (Optional Subsection)
